Mechanistic Bayesian Forecasts of COVID19

### 2020-07-26 paper.tex
i hate git

\section{Results}

@@

\begin{itemize}
\item MechBayes is uniformly better than baseline model when broken down by region and timezero.
\end{itemize}

>>>>

\section{COVID-Hub Results}

@@

\begin{figure}
  \centering
     \begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.1]{mae_results_by_time_zero.png}
    \caption{MAE by timezero}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.1]{mae_results_by_region.png}
    \caption{MAE by region}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.1]{wis_results_by_time_zero.png}
    \caption{WIS by timezero}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.1]{wis_results_by_region.png}
    \caption{WIS by region}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.1]{mae_results_by_target.png}
    \caption{WIS by timezero}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.1]{wis_results_by_target.png}
    \caption{WIS by region}
\end{subfigure}%

\caption{Scores from covid-hub.}
\label{fig:covidhub}
\end{figure}

\begin{itemize}
\item MechBayes is almost always better than baseline model when broken down by region, target, and timezero after June 1st 2020.
\item MechBayes has improved over time.
\begin{itemize}
\item First two submissions did not have detection probability random walk
\item Observations were Normally distributed on cumulative deaths
\item Switched to current model
\end{itemize}
\item Naive baseline is hard to beat
\item MechBayes is biased high. This comes from uncertainty in the random walk leading to potentially huge growth rates. 
\end{itemize}

   \section{Ablation Results}

   \begin{itemize}
   \item Model ranking is as follows
   \begin{itemize}
   \item MechBayes
   \item MechBayes-Case Observations
   \item MechBayes - no detection random walk
   \end{itemize}
   \item This ordering is inu
   \end{itemize}

\section{Discussion}
\begin{itemize}
\item Mech Bayes is a fast fully bayesian compartmental model capable of accounting for real-world modeling challenges during a pandemic.
\item Demonstrated success across regions, targets, and timezeros
\item Real-time model results show the practice of modeling during an epidemic. Results are improving.
\item Ablation studies show the results are grounded in real model improvements using historical validation.
\item Talk about how overall MAE obscures the huge geographic variability. 
\end{itemize}

\section{Conclusion}

\begin{itemize}
\item Summarize mech bayes as bayesian compartmental model
\item Further work: most of the model is about $\beta(t)$. Better methods for modeling it? Spline Etc.
\end{itemize}
